The paper on blockchain front-running

### 2018-09-20 frontrunning/Latex/sections/paper.tex
edits

% @J : intro needs lots of love.

@@

\emph{Front-running} is analogous to any course of action during which a person or entity benefits from prior access to inside or confidential market information about upcoming transactions and trades, albeit the problem can occur in both financial and non-financial systems.  In traditional exchanges, traders would gather in same physical locations to announce their position in the market, in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock. 
%In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from the advance knowledge of pending client orders. 
The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and \textit{SEC} to regulate, detect and define laws and policies to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W. Sullivan, President  CBoE).}
\end{quote}

Defining what exactly was considered illegal front-running required more knowledge of how these new markets behaved. \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running. However, the difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.

Further reading on the early details on the history and challenges of detecting and regulating front-running is extensively written by Markham~\cite{markham1988front} . %add a more recent publication?

Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002},  then again in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in options, derivatives, or other financial instruments overlying a security with a few exceptions~\cite{sec2012frontrunning, finra_2012}.

\subsection{Blockchain Front-running} \label{sec:Front Running on the Blockchains}

>>>>

% @J : intro needs lots of love.
% Jeremy: Will work on this very last, once I know what the paper is actually about :)

@@

\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information. The problem can occur in both financial and non-financial systems. In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces supply of the stock. Brokers might also frontrun their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders). Front-running is unethical and illegal in jurisdictions with mature securities regulation.

% Jeremy: I don't real;y understand the below so dropping if no one protests. 
%The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
%As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}
\end{quote}

@@

Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}. The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W. Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~\cite{sec1978optionsmarket}.

We refer the reader interested in further details on the early regulatory history of front-running to Markham~\cite{markham1988front}. Initially front-running policies applied only to certain option markets. In 2002, the rule was expanded to cover all security futures~\cite{finra_2002}. In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning, finra_2012}.

\subsection{Background on Blockchain Front-running} \label{sec:Front Running on the Blockchains}
